Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2020-01-07 draft_p2.tex
test_commit

\begin{abstract}
This study evaluates the relevance of rare-event sampling techniques to accelerate the simulation of extreme mechanical efforts exerted by a turbulent flow impinging onto a bluff body.
The main idea is to replace a long simulation by a set of much shorter ones, running in parallel, with dynamics that are replicated or pruned in order to sample large-amplitude events more frequently. 
%
Such techniques have been shown to be efficient for a wide range of problems in statistical physics, computer science, biochemistry, enabling the simulation of rare  events otherwise out of reach by direct sampling.
This work is the first application to fluid-structure interaction problems. 
%
The drag experienced by a squared obstacle placed in a turbulent flow (in two dimensions) is taken as a representative case study to investigate the performance of two major rare-event sampling algorithms, namely the \ac{ams} and the \ac{gktl} algorithms.
Practical evidence is given that the fast sweeping-time of fluid structures past the obstacle has a drastic influence on the efficiency of these two algorithms.
While it is shown that the \ac{ams} algorithm does not yield significant run-time savings, the \ac{gktl} algorithm appears to be efficient to sample extreme fluctuations of the time-averaged drag and estimate related statistics such as return times. 
%
Beyond the study of applicability of rare-event sampling techniques to a fluid-mechanical problem, this work also includes a detailed phenomenological description of extreme-drag events of a turbulent flow on a bluff body. 
\end{abstract}

>>>>

\begin{abstract}
Blabla !!! This study evaluates the relevance of rare-event sampling techniques to accelerate the simulation of extreme mechanical efforts exerted by a turbulent flow impinging onto a bluff body.
The main idea is to replace a long simulation by a set of much shorter ones, running in parallel, with dynamics that are replicated or pruned in order to sample large-amplitude events more frequently. 
%
Such techniques have been shown to be efficient for a wide range of problems in statistical physics, computer science, biochemistry, enabling the simulation of rare  events otherwise out of reach by direct sampling.
This work is the first application to fluid-structure interaction problems. 
%
The drag experienced by a squared obstacle placed in a turbulent flow (in two dimensions) is taken as a representative case study to investigate the performance of two major rare-event sampling algorithms, namely the \ac{ams} and the \ac{gktl} algorithms.
Practical evidence is given that the fast sweeping-time of fluid structures past the obstacle has a drastic influence on the efficiency of these two algorithms.
While it is shown that the \ac{ams} algorithm does not yield significant run-time savings, the \ac{gktl} algorithm appears to be efficient to sample extreme fluctuations of the time-averaged drag and estimate related statistics such as return times. 
%
Beyond the study of applicability of rare-event sampling techniques to a fluid-mechanical problem, this work also includes a detailed phenomenological description of extreme-drag events of a turbulent flow on a bluff body. 
\end{abstract}
